working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
changes
change

To evaluate heterospecific pollen effect on seed production we performed linear mixed models. The distinct heterospecific pollination treatments were compared thorugh relevelling each variable with the cross pollination treatment which was our control for optimum seed production for all the species. The different replicates of each treatment were considered as random effects. The changes of seed production across species were compared through scaling the seed production with mean 0 and standard deviation of 1 prior to the analysis. All the analysis were conducted with the statistical language `R` `r citep(citation())`.

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances). Heterospecific pollen effect was obtain through the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.

@@

Results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in **Table 2**. Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Across families we found a very similar effect but when species where look at species level they respond differently even within the same family [rephrase and maybe test statistically?](), for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine. The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial- IB Unclear](). Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases [under which treatment](). *S. lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size. *C. annuum* produced some fruits (9%) of both small and normal size and finally *S. melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.[clarify this descriptive statistics part- Also a figure with a summary of the treatments effect would be cool, or at least in the appendices]()

>>>>

To evaluate heterospecific pollen effect on seed production we performed linear mixed models. The distinct heterospecific pollination treatments were compared through relevelling each variable with the cross pollination treatment which was our control for optimum seed production for all the species. The different replicates of each treatment were considered as random effects. Seed production was scaled for all the species with mean 0 and standard deviation of 1 prior to the analysis. All the analysis were conducted with the statistical language `R` `r citep(citation())`.

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances). Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.

@@

Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Table 2**. Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.

Across families we found a very similar effect but when species where look at species level they respond differently even within the same family [rephrase and maybe test statistically?](), for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine. The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial- IB Unclear](). Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases [under which treatment](). *S. lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size. *C. annuum* produced some fruits (9%) of both small and normal size and finally *S. melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.[clarify this descriptive statistics part- Also a figure with a summary of the treatments effect would be cool, or at least in the appendices]()

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
changes
change

To evaluate heterospecific pollen effect on seed production we performed
linear mixed models. The distinct heterospecific pollination treatments
were compared thorugh relevelling each variable with the cross
pollination treatment which was our control for optimum seed production
for all the species. The different replicates of each treatment were
considered as random effects. The changes of seed production across
species were compared through scaling the seed production with mean 0
and standard deviation of 1 prior to the analysis. All the analysis were
conducted with the statistical language \texttt{R} (R Core Team 2018).

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (Euclidean distances). Heterospecific pollen
effect was obtain through the subtraction of seed production by hand
cross pollination minus seed production of the different heterospecific
pollen treatments. To find a model with the best explanatory traits we
used the function \textbf{bioenv} from R. We also conducted Mantel test
between the matrix of heterospecific pollen effect and the distance
matrix from all the traits. Moreover, we explored also the correlation
between traits and heterospecific pollen effect through generalized
mixed models where the response variable was heterospecific pollen
effect and the explanatory variable the different traits.

@@

Results of hand cross pollination, self hand pollination, natural
selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
pollen reduced seet set signifcatively with the 50-50\% heterospecific
pollen treatments for 65\% of the pairwise interactions
p\textless{}0.05. Across families we found a very similar effect but
when species where look at species level they respond differently even
within the same family \href{}{rephrase and maybe test statistically?},
for instance for two species of the Brassicaceae family \emph{Brassica
oleracea} and \emph{Eruca versicaria} we found very contrasting effects
of foreign pollen where for the first one, all donors reduce seed set
significatively and for the second, just two species did out of nine.
The 100\% foreign pollen treatments barely produced seeds or fruits
\href{}{and just for \emph{Sinapis alba} we did not find significant
differences between the hand cross pollination and one treatment with
pollen from a confamilial- IB Unclear}. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases
\href{}{under which treatment}. \emph{S. lycopersicum} seems to produced
small fruits (35\% of the treatments) independently of pollen and pollen
donor due to also apomictic treatments did, never normal size. \emph{C.
annuum} produced some fruits (9\%) of both small and normal size and
finally \emph{S. melongena} produced seedless normal fruits with just
confamilial pollen (3\%), for both species seems that fruit formation
was induced by pollen on the stigma because of lack of fruit production
with treatments that tested for apomixis.\href{}{clarify this
descriptive statistics part- Also a figure with a summary of the
treatments effect would be cool, or at least in the appendices}

>>>>

To evaluate heterospecific pollen effect on seed production we performed
linear mixed models. The distinct heterospecific pollination treatments
were compared through relevelling each variable with the cross
pollination treatment which was our control for optimum seed production
for all the species. The different replicates of each treatment were
considered as random effects. Seed production was scaled for all the
species with mean 0 and standard deviation of 1 prior to the analysis.
All the analysis were conducted with the statistical language \texttt{R}
(R Core Team 2018).

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (Euclidean distances). Heterospecific pollen
effect was obtained through the subtraction of seed production by hand
cross pollination minus seed production of the different heterospecific
pollen treatments. To find a model with the best explanatory traits we
used the function \textbf{bioenv} from R. We also conducted Mantel test
between the matrix of heterospecific pollen effect and the distance
matrix from all the traits. Moreover, we explored also the correlation
between traits and heterospecific pollen effect through generalized
mixed models where the response variable was heterospecific pollen
effect and the explanatory variable the different traits.

@@

Results of hand cross-pollination, self hand-pollination, natural
selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
pollen reduced seet set signifcatively with the 50-50\% heterospecific
pollen treatments for 65\% of the pairwise interactions
p\textless{}0.05.

Across families we found a very similar effect but when species where
look at species level they respond differently even within the same
family \href{}{rephrase and maybe test statistically?}, for instance for
two species of the Brassicaceae family \emph{Brassica oleracea} and
\emph{Eruca versicaria} we found very contrasting effects of foreign
pollen where for the first one, all donors reduce seed set
significatively and for the second, just two species did out of nine.
The 100\% foreign pollen treatments barely produced seeds or fruits
\href{}{and just for \emph{Sinapis alba} we did not find significant
differences between the hand cross pollination and one treatment with
pollen from a confamilial- IB Unclear}. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases
\href{}{under which treatment}. \emph{S. lycopersicum} seems to produced
small fruits (35\% of the treatments) independently of pollen and pollen
donor due to also apomictic treatments did, never normal size. \emph{C.
annuum} produced some fruits (9\%) of both small and normal size and
finally \emph{S. melongena} produced seedless normal fruits with just
confamilial pollen (3\%), for both species seems that fruit formation
was induced by pollen on the stigma because of lack of fruit production
with treatments that tested for apomixis.\href{}{clarify this
descriptive statistics part- Also a figure with a summary of the
treatments effect would be cool, or at least in the appendices}
